---
title       : Predicting Gas Mileage Per Gallon
subtitle    : Using Car Weight, Number of Engine, Transmission Type and Horsepower
author      : Yew Wah
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- 

## Inputs
Standard R distributions typically include the "***mtcars***" dataset. It contains data on 32 automobile models from 1973-1974.
<p>
There are three attributes that are of interest for this study:
* wt - weight of the car in U.S. tons
* cyl - number of cylinders in the car's engine
* hp - Horsepower
* am - Transmission Type(Automatic or Manual)
* mpg - gas mileage (U.S. miles per U.S. gallon)

--- .class #id 

## The Model
We can easily create a linear model to estimate gas mileage given
a car's weight and the number of cylinders in its engine:
```{r}
model <- lm(mpg ~ wt + cyl + hp + am, data=mtcars)
model
```

--- .class #id 

## Results Analysis

Proof of why we chose this model
```{r}
model1 <- lm(mpg~., data = mtcars)
model2 <- lm(mpg ~ wt + cyl, data=mtcars)
anova(model, model1, model2)
```
The p-value obtained is highly significant but the workings are not shown due to space constrains

--- .class #id

## Interactive Demonstration

The following link provides an interactive demonstration of this model:    

http://yewwah.github.io/slides_datapdts

You will be able to set the number of cylinders, the weight of
the car, the transmission type and horsepower and see where the resulting predicted mileage fits in with
the rest of the cars.


